### 2018-08-13 introduction.tex
huff edits

Liquid-fueled systems present a challenge to existing neutron transport and 
depletion tools which are typically designed to simulate solid-fueled reactors.  
To handle the material flows and potential online removal and feed of 
liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP} 
\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
this approach, recent tools from universities and research institutions can 
approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis 
and couple external tools to neutron transport and depletion codes take into 
account continuous feeds and removals in \glspl{MSR}. Four of these efforts are 
listed in table~\ref{tab:fs_codes}.

>>>>

Liquid-fueled systems present a challenge to existing neutron transport and 
depletion tools which are typically designed to simulate solid-fueled reactors.  
To handle the material flows and potential online removal and feed of 
liquid-fueled systems, early \gls{MSR} simulation methods at \gls{ORNL} 
integrated neutronics and fuel cycle codes (i.e., \gls{ROD} 
\cite{bauman_rod:_1971}) into operational plant tools (i.e., \gls{MRPP} 
\cite{kee_mrpp:_1976}) for \gls{MSR} and reprocessing system design.  Based on 
this approach, recent tools from universities and research institutions can 
approximate online refueling \cite{serp_molten_2014}.  Recent research efforts 
in Europe and Asia mainly focus on fast spectrum reactor fuel cycle analysis. 
These  couple external tools to neutron transport while depletion codes take into 
account continuous feeds and removals in \glspl{MSR}. A summary of recent 
efforts are listed in table~\ref{tab:fs_codes}.
